Supplement: Autopolyploid establishment through polygenic adaptation

### 2025-05-31 doc/paper/paper.tex
update

    \begin{document}
    \title{Autopolyploid establishment through polygenic adaptation}
    \author[1]{Arthur Zwaenepoel\thanks{arthur.zwaenepoel@uantwerpen.be}}
    \affil[1]{\footnotesize Department of Biology, University of Antwerp, 2020 Antwerp, Belgium}
    %\author{}
    \date{\vspace{-5ex}}
    \maketitle
    \begin{abstract}
    We define the infinitesimal model of quantitative genetics for the inheritance
        of an additive quantitative trait in a mixed-ploidy population consisting
        of diploid, triploid and autotetraploid individuals producing haploid and
        diploid gametes.
        We implement efficient simulation methods and use these to study the
        quantitative genetics of mixed-ploidy populations and the establishment of
        autotetraploids in a new habitat.
        We show that, when migration from the source population is rare,
        autotetraploids are more likely to establish in the new habitat 
        than diploids under a very broad range of conditions, but that this
        is unlikely to sufficiently counter the scarcity of tetraploid founders
        when the source is predominantly diploid.
        We assess in more detail how minority cytotype exclusion interacts with
        migration load in the establishment process and evaluate the impact of
        additional sources of prezygotic isolation, specifically selfing and
        assortative mating, on the relative establishment probabilities of the
        different cytotypes in the presence of maladaptive migration.
        In the discussion we consider how inbreeding depression may impact our
        findings.

@@

    \begin{table}[t]
    \caption{Glossary of the notation used in the main text.
    } \label{tbl:glossary}
    \centering
    \small
    \begin{tabularx}{\linewidth}{lX}
    \cline{1-2}
    \textbf{notation}   & \textbf{description}   \\ \cline{1-2}
    $N$ & total population size\\
    $N_k$ & population size of the $k$-ploid cytotype \\
    $\pi_k$ & deterministic equilibrium frequency of the $k$-ploid cytotype \\
    $u$ & probability of unreduced gamete formation ($u=u_{22}=1-u_{42}$)\\
    $v$ & probability that a triploid produces a haploid/diploid gamete
      ($v=u_{31}=u_{32}$)\\
    $m$ & expected number of migrants per generation arriving in the new habitat \\
    $z_i$ & trait value of individual $i$ \\
    $c_i$ & ploidy level of individual $i$ \\
    $g_i$ & ploidy level of gamete produced by individual $i$ in a particular cross\\
    $V$ & segregation variance in the reference diploid population \\
    $V_{i,k}$ & gametic segregation variance associated with the production of a
      $k$-ploid gamete by individual $i$ \\
    $\Vx_k$ & genetic variance associated with a haploid genome in the $k$-ploid
      reference population (i.e. a $k$-ploid non-inbred population at HWLE) \\
    $\beta_{k}$ & scaling factor for allelic effects in $k$-ploids \\
    $F_i$ & inbreeding coefficient in individual $i$ \\
    $\Phi_{ij}$ & coancestry coefficient for individuals $i$ and $j$ \\
    $\alpha_k$ & probability that the two genes at a locus in a diploid gamete
      formed by a $k$-ploid individual descend from the same parental gene copy\\
    $\gamma$ & strength of directional selection in the new habitat\\
    $\theta$ & trait value beyond which the growth rate becomes positive in the new
        habitat \\ 
    $w_{ij}$ & fitness of parental pair $(i,j)$ (expected fitness of
        offspring of pair $(i,j)$)\\
    $w_{ij}^{kl}$ & expected fitness of offspring of parental pair $(i,j)$ when
    $i$ contributes a $k$-ploid gamete and $j$ contributes a $l$-ploid gamete \\
    $\sigma_k$ & rate of self-fertilization in $k$-ploids \\
    $\rho_k$ & probability of assortative mating in $k$-ploids \\
    \cline{1-2}
    \end{tabularx}%
    \end{table}

@@

    In generation $t$, $M(t)$ migrant individuals arrive on an island (the new
    habitat) joining $N^\ast(t)$ resident individuals, where $M(t)$ is Poisson
    distributed with mean $m$, and $N^\ast(0)=0$ unless stated otherwise. 
    The migrant individuals are assumed to be unrelated to the resident
    individuals.
    After migration there are $N(t) = N^\ast(t) + M(t)$ individuals on the island
    which reproduce sexually, and the offspring thus produced survives until the
    next generation with a probability determined by their trait value.
    Note that this corresponds to a life cycle where selection occurs before
    migration within a generation.
    In the basic model, random selfing is allowed (but see below for a model with
    self-incompatibility).
    We assume the trait is under directional selection, with fitness $w(z) =
    e^{\gamma(z - \theta)}$, where $\gamma$ is the intensity of directional
    selection and $\theta$ is the trait value for which the growth rate of the
    island population becomes positive.
    As the population becomes better adapted, eventually, some form of density
    regulation must limit its growth.
    We ignore density regulation throughout and focus on the initial establishment
    phase, defining establishment as reaching a population of size 100.

    Again following \cite{barton2018}, we simulate the model by first calculating
    the fitness of each parental pair $(i,j)$, which is the expected fitness of
    offspring of this pair
    \begin{equation}
      w_{ij}
        = \sum_{k=1}^2\sum_{l=1}^2 w_{ij}^{kl}
        = \sum_{k=1}^2\sum_{l=1}^2 u_{c_{i},k}u_{c_{j},l}
            \Ex\left[e^{\gamma(Z_{ij}^{kl} - \theta)}\right]
    \end{equation}
    The expectation on the right hand side can be calculated from \cref{eq:oneline}
    using the moment-generating function of the Gaussian, i.e.
    \begin{equation}
        \Ex\left[e^{\gamma(Z_{ij}^{kl} - \theta)}\right] 
        = e^{\gamma \left(\overline{z_{ij}^{kl}} -\theta\right) +
        \frac{\gamma^2}{2}
        V_{ij}^{kl}} 
        \label{eq:Ew}
    \end{equation}
    Having calculated the $w_{ij}$, the number of offspring surviving into the next
    generation is calculated as $N^\ast(t+1) = \sum_{i,j}w_{ij}/N(t)$.
    Next, $N^\ast(t+1)$ offspring individuals are obtained by sampling parental
    pairs and gametes proportional to $w_{ij}^{kl}$, and sampling a trait value
    from a Gaussian distribution with mean $\overline{z_{ij}^{kl}} + \gamma
    V_{ij}^{kl}$ and variance $V_{ij}^{kl}$.

@@

    We model partial self-fertilization by assuming that a proportion
    $\sigma_{c_i}$ of the ovules of individual $i$ with ploidy level $c_i$ are
    fertilized by self-pollen, while the remaining proportion $1-\sigma_{c_i}$ are
    fertilized by randomly sampled pollen (which may be self-pollen with
    probability $1/N$). 
    That is, the expected number of offspring from individual $i$ as mother
    surviving after selection is
    \begin{equation}
    \Ex[w_i] = \sigma_{c_i} w_{ii} +
      (1-\sigma_{c_i})\left[\frac{1}{N}\sum_{j=1}^N w_{ij}\right]
    \end{equation}
    We hence assume no pollen limitation (all outcrossing ovules are fertilized),
    and no pollen discounting (the probability of being a father is unaffected by
    an individual's selfing rate).
    When modeling self-incompatibility, we assume there is no intrinsic
    disadvantage to self-incompatibility, except when there is only a single
    individual in the population, i.e.
    \begin{equation}
    \Ex[w_i] = \begin{cases}
        \frac{1}{N-1}\sum_{j \ne i }w_{ij} & \text{if } N > 1\\ 
        0 & \text{if } N=1 \end{cases}
    \end{equation}

    We model assortative mating by ploidy level in a similar way, assuming that a
    fraction $\rho_{c_i}$ of the ovules of individual $i$ are fertilized by pollen
    sampled from the $c_i$-ploid portion of the population, while a fraction
    $1-\rho_{c_i}$ is fertilized by pollen randomly sampled from the entire
    population.
    \begin{equation}
    \Ex[w_i] = \rho_{c_i} \frac{1}{N_{c_{i}}} \sum_{j=1}^N \delta_{c_i,c_j}w_{ij}
     + (1-\rho_{c_i})
    \left[\frac{1}{N}\sum_{j=1}^N w_{ij}\right]
    \end{equation}
    Where $\delta_{x,y}$ is the Kronecker delta function.

@@

    Individual-based simulations for the mixed-ploidy infinitesimal model were
    implemented in Julia \citep{julia}.
    %Documented code and simulation notebooks are available at \url{[anonymized]}.
    Documented code and simulation notebooks are available at
    \url{https://github.com/arzwa/InfGenetics}.

@@

While in this study we focused on polyploid establishment in a peripheral
habitat and how this is affected by migration from a diploid source, the
mixed-ploidy infinitesimal framework could be used to address many other
eco-evolutionary questions that arise in the study of mixed-ploidy populations.
For instance, it could be of interest to develop a complicated individual-based
model along the lines of \cite{oswald2011} to study the effects of selfing,
assortative mating and competition on establishment and coexistence of
tetraploids within diploid populations, but where the focal trait that
determines fitness and assortative mating is not controlled by a few
large-effect loci (as in \cite{oswald2011}), but many loci of small effect.
Similarly, our model could be straightforwardly extended to include population
regulation and stabilizing selection, which would allow us to study polyploid
establishment along an environmental gradient and the potential of
polyploidization to promote range expansions \citep{polechova2015}.

>>>>

    \begin{document}
    \title{Autopolyploid establishment through polygenic adaptation}
    \author[1]{Arthur Zwaenepoel\thanks{arthur.zwaenepoel@uantwerpen.be}}
    \affil[1]{\footnotesize Department of Biology, University of Antwerp, 2020 Antwerp, Belgium}
    \date{\vspace{-5ex}}
    \maketitle
    \begin{abstract}
    We define the infinitesimal model of quantitative genetics for the inheritance
        of an additive quantitative trait in a mixed-ploidy population consisting
        of diploid, triploid and autotetraploid individuals producing haploid and
        diploid gametes.
        We implement efficient simulation methods and use these to study the
        quantitative genetics of mixed-ploidy populations and the establishment of
        autotetraploids in a new habitat.
        We show that, when migration from the source population is rare,
        autotetraploids are more likely to establish in the new habitat 
        than diploids under a very broad range of conditions, but that this
        is unlikely to sufficiently counter the scarcity of tetraploid founders
        when the source is predominantly diploid.
        We assess in more detail how minority cytotype exclusion interacts with
        migration load in the establishment process and evaluate the impact of
        additional sources of prezygotic isolation, specifically selfing and
        assortative mating, on the relative establishment probabilities of the
        different cytotypes in the presence of maladaptive migration.
        In the discussion we consider how inbreeding depression may impact our
        findings.

@@

    \begin{table}[t]
    \caption{Glossary of the notation used in the main text.
    } \label{tbl:glossary}
    \centering
    \small
    \begin{tabularx}{\linewidth}{lX}
    \cline{1-2}
    \textbf{notation}   & \textbf{description}   \\ \cline{1-2}
    $N$ & total population size\\
    $N_k$ & population size of the $k$-ploid cytotype \\
    $\pi_k$ & deterministic equilibrium frequency of the $k$-ploid cytotype \\
    $u$ & probability of unreduced gamete formation ($u=u_{22}=1-u_{42}$)\\
    $v$ & probability that a triploid produces a haploid/diploid gamete
      ($v=u_{31}=u_{32}$)\\
    $m$ & expected number of migrants per generation arriving in the new habitat \\
    $z_i$ & trait value of individual $i$ \\
    $c_i$ & ploidy level of individual $i$ \\
    $g_i$ & ploidy level of gamete produced by individual $i$ in a particular cross\\
    $V$ & segregation variance in the reference diploid population \\
    $V_{i,k}$ & gametic segregation variance associated with the production of a
      $k$-ploid gamete by individual $i$ \\
    $\Vx_k$ & genetic variance associated with a haploid genome in the $k$-ploid
      reference population (i.e. a $k$-ploid non-inbred population at HWLE) \\
    $\beta_{k}$ & scaling factor for allelic effects in $k$-ploids \\
    $F_i$ & inbreeding coefficient in individual $i$ \\
    $\Phi_{ij}$ & coancestry coefficient for individuals $i$ and $j$ \\
    $\alpha_k$ & probability that the two genes at a locus in a diploid gamete
      formed by a $k$-ploid individual descend from the same parental gene copy\\
    $\gamma$ & strength of directional selection in the new habitat\\
    $\theta$ & trait value beyond which the growth rate becomes positive in the new
        habitat \\ 
    $w_{ij}$ & fitness of parental pair $(i,j)$ (expected zygotic fitness of
        offspring of pair $(i,j)$)\\
    $w_{ij}^{kl}$ & expected fitness of zygote from parental pair $(i,j)$ when
        $i$ contributes a $k$-ploid gamete and $j$ contributes a $l$-ploid gamete \\
    $w_i$ & expected number of offspring from individual $i$ surviving to
        reproductive age \\
    $\sigma_k$ & rate of self-fertilization in $k$-ploids \\
    $\rho_k$ & probability of assortative mating in $k$-ploids \\
    \cline{1-2}
    \end{tabularx}%
    \end{table}

@@

    In generation $t$, $M(t) \sim \mathrm{Poisson}(m)$ migrant individuals
    arrive on an island (the new habitat) joining $N^\ast(t)$ resident
    individuals.
    We assume $N^\ast(0)=0$ unless stated otherwise. 
    The migrant individuals are assumed to be unrelated to the resident
    individuals.
    After migration there are $N(t) = N^\ast(t) + M(t)$ individuals on the
    island.
    These individuals reproduce sexually by random mating (allowing random
    selfing, see below for modifications involving partial selfing and
    assortative mating) to produce a large (effectively infinite) number of
    zygotes, of which $N^\ast(t+1)$ survive to reproductive age with a
    probability proportional to individual fitness, where $N^\ast(t+1)$ is
    Poisson distributed with mean $N(t)\overline{W}$ and $\overline{W}$ is the
    mean fitness among zygotes.
    We assume the trait to be under directional selection, with the fitness of a
    zygote with trait value $z$ given by $w(z) = e^{\gamma(z - \theta)}$, where
    $\gamma$ is the intensity of directional selection and $\theta$ is the
    trait value for which the growth rate of the island population becomes
    positive.
    As the population becomes better adapted, eventually, some form of density
    regulation must limit its growth.
    We ignore density regulation throughout and focus on the initial establishment
    phase, defining establishment as reaching a population of size 100.
    Note that this model corresponds to a life cycle where selection occurs
    before migration within a generation.

    Again following \cite{barton2018}, we simulate the model by first calculating
    the fitness of each parental pair $(i,j)$, which is defined as the expected
    fitness of a random zygote derived from this pair
    \begin{equation}
      w_{ij}
        = \sum_{k=1}^2\sum_{l=1}^2 w_{ij}^{kl}
        = \sum_{k=1}^2\sum_{l=1}^2 u_{c_{i},k}u_{c_{j},l}
            \Ex\left[e^{\gamma(Z_{ij}^{kl} - \theta)}\right] \label{eq:wij}
    \end{equation}
    The expected number of offspring individuals of an individual $i$
    surviving to reproductive age is then $w_i = \frac{1}{N(t)}\sum_j w_{ij}$.
    The expectation on the right hand side of \cref{eq:wij} can be calculated
    from \cref{eq:oneline} using the moment-generating function of the
    Gaussian, i.e.
    \begin{equation}
        \Ex\left[e^{\gamma(Z_{ij}^{kl} - \theta)}\right] 
        = e^{\gamma \left(\overline{z_{ij}^{kl}} -\theta\right) +
        \frac{\gamma^2}{2}
        V_{ij}^{kl}} 
        \label{eq:Ew}
    \end{equation}
    Having calculated the $w_{ij}$, the number of offspring surviving into the next
    generation $N^\ast(t+1)$ is sampled from a Poisson distribution with mean
    $N(t)\overline{W} = \sum_i w_i = \sum_{i,j}w_{ij}/N(t)$.
    Offspring cytotypes and trait values are then determined by sampling
    parental pairs and gametes proportional to $w_{ij}^{kl}$, and sampling a
    trait value from the offspring trait value distribution conditional on
    survival to reproductive age, which is Gaussian with mean
    $\overline{z_{ij}^{kl}} + \gamma V_{ij}^{kl}$ and variance $V_{ij}^{kl}$ .

@@

    We model partial self-fertilization by assuming that a proportion
    $\sigma_{c_i}$ of the ovules of individual $i$ with ploidy level $c_i$ are
    fertilized by self-pollen, while the remaining proportion $1-\sigma_{c_i}$ are
    fertilized by randomly sampled pollen (which may be self-pollen with
    probability $1/N$). 
    That is, the expected number of offspring from individual $i$ as mother
    surviving after selection is
    \begin{equation}
    w_i = \sigma_{c_i} w_{ii} +
      (1-\sigma_{c_i})\left[\frac{1}{N}\sum_{j=1}^N w_{ij}\right]
    \end{equation}
    We hence assume no pollen limitation (all outcrossing ovules are fertilized),
    and no pollen discounting (the probability of being a father is unaffected by
    an individual's selfing rate).
    When modeling self-incompatibility, we assume there is no intrinsic
    disadvantage to self-incompatibility, except when there is only a single
    individual in the population, i.e.
    \begin{equation}
    w_i = \begin{cases}
        \frac{1}{N-1}\sum_{j \ne i }w_{ij} & \text{if } N > 1\\ 
        0 & \text{if } N=1 \end{cases}
    \end{equation}

    We model assortative mating by ploidy level in a similar way, assuming that a
    fraction $\rho_{c_i}$ of the ovules of individual $i$ are fertilized by pollen
    sampled from the $c_i$-ploid portion of the population, while a fraction
    $1-\rho_{c_i}$ is fertilized by pollen randomly sampled from the entire
    population.
    \begin{equation}
    w_i = \rho_{c_i} \frac{1}{N_{c_{i}}} \sum_{j=1}^N \delta_{c_i,c_j}w_{ij}
     + (1-\rho_{c_i})
    \left[\frac{1}{N}\sum_{j=1}^N w_{ij}\right]
    \end{equation}
    Where $\delta_{x,y}$ is the Kronecker delta function.

@@

    Individual-based simulations for the mixed-ploidy infinitesimal model were
    implemented in Julia \citep{julia}.
    Documented code and simulation notebooks are available at \url{https://github.com/arzwa/InfGenetics}.

@@

While in this study we focused on polyploid establishment in a peripheral
habitat and how this is affected by migration from a diploid source, the
mixed-ploidy infinitesimal framework could be used to address many other
eco-evolutionary questions that arise in the study of mixed-ploidy populations.
For instance, it could be of interest to develop an individual-based
model along the lines of \cite{oswald2011} to study competitive exclusion
versus coexistence of cytotypes in mixed-ploidy populations with partial
selfing, assortative mating, competition, \textit{etc.}, but where the focal
trait that determines the various fitness components is not controlled by a few
large-effect loci (as in \cite{oswald2011}), but many loci of small effect.
Similarly, our model could be straightforwardly extended to include population
regulation and stabilizing selection, which would allow us to study polyploid
establishment along an environmental gradient and the potential of
polyploidization to promote range expansions \citep{polechova2015}.

### 2025-05-31 doc/paper/supp.tex
update

\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{/home/arzwa/dev/InfGenetics/doc/img/finsvsinf-polyploids-validation.pdf}
\caption{
Validation of the autotetraploid and triploid infinitesimal model by a
comparison against the discrete locus model with $L=500$ additive loci, showing
the average phenotypic variance in each generation averaged over 10 replicate
simulations for both models.
We assume the initial phenotypic variance to be one for all simulations, and
all replicates are initialized randomly in accordance with this initial
phenotypic variance.
Allelic effects for the discrete locus model are sampled from a Gaussian with
mean $0$ and variance $1/2L$.
\label{fig:fininf}}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{/home/arzwa/vimwiki/build/img/2023-10-23/mixedploidy-Vz.pdf}
\caption{Comparison of the mixed-ploidy infinitesimal model with the
\(L\)-locus model, for \(L=500,100,50\) and \(20\). The decline in the
genetic variance \(V_z\) within each cytotype due to drift is shown. The
transparent lines show the complete simulation, whereas the solid line
shows the same data but smoothed in overlapping windows of 20
generations. We assume \(N=500, u=v=0.08\) and no selection. In the top
row where \(\beta_k^2=1, \alpha_k=0\), the equilibrium variance in the
absence of inbreeding in triploids is 2/3 that of diploids, and in
tetraploids it is twice that in diploids. In the middle row,
\(\beta_3^2=2/3\) and \(\beta_4^2=1/2\), so that the equilibrium
variance in the absence of inbreeding is equal across cytotypes. In the
bottom row, \(\alpha_2= \alpha_3 =1/2\) and \(\alpha_4=1/6\), causing an
immediate increase in the genetic variance in higher cytotypes, but also
accelerated inbreeding. \label{fig:vz}}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=\linewidth]{/home/arzwa/vimwiki/build/img/2023-10-23/mixedploidy-F.pdf}
\caption{Average inbreeding coefficient \(\bar{F}\) in each cytotype in
a mixed-ploidy population for different values of \(\alpha\) (we assume
\(\alpha_k=\alpha\), where \(\alpha_k\) is the probability that a
diploid gamete produced by a \(k\)-ploid cytotype contains two copies of
the same parental gene at a random locus). We assume \(N=500, u=v=0.08\)
and no selection.}\label{fig:f1}
\end{figure}

\begin{figure}
\includegraphics[width=0.9\linewidth]{/home/arzwa/dev/InfGenetics/doc/img/estwmigration-dr-check.pdf}
\caption{
    Nonzero $\alpha_k$ parameters increase the tetraploid establishment
    probability, but mainly due to $\alpha_2$, which increases the segregation
    variance associated with the formation of diploid gametes by diploids.
    All other parameters and simulation details are as in \cref{m-fig:estwmig}.
\label{fig:suppdr}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\linewidth]{/home/arzwa/vimwiki/build/img/2023-10-13/g1diff.pdf}
\caption{
Deterministic mixed-ploidy equilibrium. The left plot shows the stable (solid
lines) and unstable (dashed lines) equilibria for the proportion of haploid
gametes in the gamete pool $g_1$ as a function of $u$ for different values of
$v$. The middle plot shows the relationship between $\Delta g_1 = g_1' - g_1$
and $g_1$. The zeros of this graph are the fixed points of the dynamical system
and are indicated by the hollow (unstable equilibrium) and solid (stable
equilibrium) dots. The rightmost plot shows the region of parameter space where
a stable mixed-ploidy equilibrium exist.
\label{fig:g1diff}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{/home/arzwa/vimwiki/build/img/2023-10-22/timetodiploidancestord.pdf}
\caption{Expected time to diploid ancestry. The solid lines show
\(\Ex[T_4]\), i.e.~the expected time since being inherited from a
diploid ancestor for a random gene in a tetraploid individual at
equilibrium, for different values of \(v\) (half the triploid
fertility). The dashed lines show \(\Ex[T_3]\), i.e.~the same quantity
for a gene sampled from a triploid. Note that \(\Ex[T]\) blows up
whenever \(u\) and \(v\) exceed their critical value for tetraploid
establishment. \label{fig:ttdip}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{/home/arzwa/vimwiki/build/img/2023-10-13/mixedploidy-F-Ne.pdf}
\caption{The evolution of \(\bar{F}\) in the mixed-ploidy population and
in the diploid subpopulation are shown for different values of \(u\) and
associated values of \(N\), keeping \(N_e = (1-2u)N\) constant at 200.
We assume \(u=v\). All lines coincide almost completely and are
indistinguishable from \(1-e^{-t/2N_e}\). Results are shown for
\(\alpha_k=1/6\). As \(\alpha_k\) decreases to 0, \(\bar{F}\) in the
mixed-ploidy population becomes completely indistinguishable from
\(\bar{F}\) in the diploid subpopulation.}\label{fig:fNe}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{/home/arzwa/dev/InfGenetics/doc/img/mixeq.pdf}
\caption{
    Equilibrium trait value distribution for diploids, triploids and
    tetraploids.
    The simulated equilibrium distribution, the small $u$ approximation and the
    monocytotypic equilibrium distribution are shown for all three cytotypes.
    The diploid monocytotypic distribution $\Normal(0,2V)$ is shown everywhere
    as a reference. Here we assumed $\beta_3 = \beta_4 = 1$ and $\alpha_2 =
    1/2, \alpha_3 = 1/4$ and $\alpha_4 = 1/6$.
\label{fig:mixeq}}
\end{figure}

>>>>

\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{/home/arzwa/dev/InfGenetics/doc/supp_img/finsvsinf-polyploids-validation.pdf}
\caption{
Validation of the autotetraploid and triploid infinitesimal model by a
comparison against the discrete locus model with $L=500$ additive loci, showing
the average phenotypic variance in each generation averaged over 10 replicate
simulations for both models.
We assume the initial phenotypic variance to be one for all simulations, and
all replicates are initialized randomly in accordance with this initial
phenotypic variance.
Allelic effects for the discrete locus model are sampled from a Gaussian with
mean $0$ and variance $1/2L$.
\label{fig:fininf}}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{/home/arzwa/dev/InfGenetics/doc/supp_img/mixedploidy-Vz.pdf}
\caption{Comparison of the mixed-ploidy infinitesimal model with the
\(L\)-locus model, for \(L=500,100,50\) and \(20\). The decline in the
genetic variance \(V_z\) within each cytotype due to drift is shown. The
transparent lines show the complete simulation, whereas the solid line
shows the same data but smoothed in overlapping windows of 20
generations. We assume \(N=500, u=v=0.08\) and no selection. In the top
row where \(\beta_k^2=1, \alpha_k=0\), the equilibrium variance in the
absence of inbreeding in triploids is 2/3 that of diploids, and in
tetraploids it is twice that in diploids. In the middle row,
\(\beta_3^2=2/3\) and \(\beta_4^2=1/2\), so that the equilibrium
variance in the absence of inbreeding is equal across cytotypes. In the
bottom row, \(\alpha_2= \alpha_3 =1/2\) and \(\alpha_4=1/6\), causing an
immediate increase in the genetic variance in higher cytotypes, but also
accelerated inbreeding. \label{fig:vz}}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=\linewidth]{/home/arzwa/dev/InfGenetics/doc/supp_img/mixedploidy-F.pdf}
\caption{Average inbreeding coefficient \(\bar{F}\) in each cytotype in
a mixed-ploidy population for different values of \(\alpha\) (we assume
\(\alpha_k=\alpha\), where \(\alpha_k\) is the probability that a
diploid gamete produced by a \(k\)-ploid cytotype contains two copies of
the same parental gene at a random locus). We assume \(N=500, u=v=0.08\)
and no selection.}\label{fig:f1}
\end{figure}

\begin{figure}
\includegraphics[width=0.9\linewidth]{/home/arzwa/dev/InfGenetics/doc/supp_img/estwmigration-dr-check.pdf}
\caption{
    Nonzero $\alpha_k$ parameters increase the tetraploid establishment
    probability, but mainly due to $\alpha_2$, which increases the segregation
    variance associated with the formation of diploid gametes by diploids.
    All other parameters and simulation details are as in \cref{m-fig:estwmig}.
\label{fig:suppdr}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\linewidth]{/home/arzwa/dev/InfGenetics/doc/supp_img/g1diff.pdf}
\caption{
Deterministic mixed-ploidy equilibrium. The left plot shows the stable (solid
lines) and unstable (dashed lines) equilibria for the proportion of haploid
gametes in the gamete pool $g_1$ as a function of $u$ for different values of
$v$. The middle plot shows the relationship between $\Delta g_1 = g_1' - g_1$
and $g_1$. The zeros of this graph are the fixed points of the dynamical system
and are indicated by the hollow (unstable equilibrium) and solid (stable
equilibrium) dots. The rightmost plot shows the region of parameter space where
a stable mixed-ploidy equilibrium exist.
\label{fig:g1diff}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{/home/arzwa/dev/InfGenetics/doc/supp_img/timetodiploidancestord.pdf}
\caption{Expected time to diploid ancestry. The solid lines show
\(\Ex[T_4]\), i.e.~the expected time since being inherited from a
diploid ancestor for a random gene in a tetraploid individual at
equilibrium, for different values of \(v\) (half the triploid
fertility). The dashed lines show \(\Ex[T_3]\), i.e.~the same quantity
for a gene sampled from a triploid. Note that \(\Ex[T]\) blows up
whenever \(u\) and \(v\) exceed their critical value for tetraploid
establishment. \label{fig:ttdip}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{/home/arzwa/dev/InfGenetics/doc/supp_img/mixedploidy-F-Ne.pdf}
\caption{The evolution of \(\bar{F}\) in the mixed-ploidy population and
in the diploid subpopulation are shown for different values of \(u\) and
associated values of \(N\), keeping \(N_e = (1-2u)N\) constant at 200.
We assume \(u=v\). All lines coincide almost completely and are
indistinguishable from \(1-e^{-t/2N_e}\). Results are shown for
\(\alpha_k=1/6\). As \(\alpha_k\) decreases to 0, \(\bar{F}\) in the
mixed-ploidy population becomes completely indistinguishable from
\(\bar{F}\) in the diploid subpopulation.}\label{fig:fNe}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{/home/arzwa/dev/InfGenetics/doc/supp_img/mixeq.pdf}
\caption{
    Equilibrium trait value distribution for diploids, triploids and
    tetraploids.
    The simulated equilibrium distribution, the small $u$ approximation and the
    monocytotypic equilibrium distribution are shown for all three cytotypes.
    The diploid monocytotypic distribution $\Normal(0,2V)$ is shown everywhere
    as a reference. Here we assumed $\beta_3 = \beta_4 = 1$ and $\alpha_2 =
    1/2, \alpha_3 = 1/4$ and $\alpha_4 = 1/6$.
\label{fig:mixeq}}
\end{figure}
